---
title: "report_example"
author: ""
date: ""
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```


## Data-set and main information needed

about: time-variables, modeled - variables, imputed-variables

Assume a data-frame has been built.

Example for this run: 

```{r data set choice, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)

## main data set as a data.frame
#df <- 

##data sets which need to be compared (could be same data measured at different moments in time), as data.frames
#df1<- 
#df2<-

##time series we need to explore:
#tsuniv
#tsmultiv

```

## Data view

```{r overview, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
view_data(df)

```

Section 2: Univariate analysis

```{r univariate, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
view_univar(df)
```


## Multivariate analysis

```{r multivariate, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
view_multivar(df)
```


## Outliers' detection

```{r outliers, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
view_outliers(df)
```


## Variability in data

```{r variability, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
rev_variability(df)
```


## Checking assumptions about data
```{r assumptions about data, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
check_assumptions(df1,df2)
```

## Association rules discovery
```{r association rules, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
view_assoc(df)
```

## Clusters identification
```{r clusters, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
view_clusters(df)
```

## Reviewing models
```{r models, glm or ts: residuals and goodness of fit, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
# if a glm type of model, then
rev_model(model_a)
#if a time series model, then
#rev_model_ts(model_a)
```

## Reviewing time series characteristics
```{r time series characteristics: univariate and multivariate, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
#for all time series, univariate
rev_ts_univ(tsuniv)
#for any multivariate time series
rev_ts_multiv(tsmultiv)
```





